Panel econometrics: introduction

### 2021-03-11 Chap-Formalia.Rmd
Global chunk options angeglichen

```{r include=FALSE}
knitr::opts_chunk$set(comment = "#>")
knitr::opts_chunk$set(
  out.height = '75%', out.width = '75%', fig.align = 'center') 
```

>>>>

```{r include=FALSE}
knitr::opts_chunk$set(comment = "#>", warning = F, message = F)
knitr::opts_chunk$set(
  out.height = '75%', out.width = '75%', fig.align = 'center') 
```
